Figure Extra

### 2023-07-31 Figures/Figures_nonTCGA.Rmd
corrrect change of name Figures_nonTCGA.Rmd

load( "/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/meyloma_ludo/meyloma.RData")
truth_Nakamura2018 <- as_tibble(FACS_Nakamura2018_mean, rownames = "Samples") %>%  mutate(Samples = as.numeric(Samples))

@@

corr <- benchmark_corrplots(deconv_data = deconv_Nakamura2018, true_estimates = truth_Nakamura2018, dict = dict_Nakamura2018, key = "Samples", title = "test")
corr
```

>>>>

load( "/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/meyloma_ludo/meyloma.RData")
truth_Nakamura2018 <- as_tibble(FACS_Thomas_mean, rownames = "Samples") %>%  mutate(Samples = as.numeric(Samples))

@@

corr <- benchmark_corrplots(deconv_data = deconv_Nakamura2018, true_estimates = truth_Nakamura2018, dict = dict_Nakamura2018, key = "Samples", title = "Nakamura et al. 2018")
corr
```
